% -------------------------------------------------------
% Challenge Level 1 - Logical
% -------------------------------------------------------
\section{Challenge 1 Level 1 (C1L1): Logical}

For this challenge, two bugs were encountered, referred to as \textbf{1) Undefined Register} and \textbf{2) Incorrect Operand}. Both issues are presented below:

% ---------------------------
% BUG1
% ---------------------------
\subsection{Bug 1: Undefined Register}

\subsubsection{Cause}

The instruction, which is shown in Listing \ref{lst:invalid_reg} on line 15852 in ``test.S," contains a bug. RISC-V provides a standard set of 
register names, such as \texttt{x0}, \texttt{x1}, ..., \texttt{x31}, which are 32 general-purpose registers. These 
registers are named: zero, ra, sp, gp, tp, t0, t1, ..., s0, s1, ..., a0, a1, etc., and are valid registers. Since \texttt{z4} does not exist, the compiler returns an error.

\begin{listing}[h]
\caption{Invalid register instruction.}
\label{lst:invalid_reg}
\begin{minted}[frame=single]{nasm}
and s7, ra, z4 # line 15852 in test.S
\end{minted}
\end{listing}

\subsubsection{Solution}

In the test context, any of the valid registers can be used. Randomly, \texttt{z4} was replaced with the valid register \texttt{s4}, as presented in Listing \ref{lst:invalid_reg_fix}. Note that, in a real application, the appropriate valid register should be chosen.

\begin{listing}[h]
\caption{Fix Listing \ref{lst:invalid_reg} instruction.}
\label{lst:invalid_reg_fix}
\begin{minted}[frame=single]{nasm}
and s7, ra, s4 # line 15852 in test.S
\end{minted}
\end{listing}

% ---------------------------
% BUG2
% ---------------------------
\subsection{Bug 2: Incorrect Operand}

\subsubsection{Cause}

The instruction in ``test.S" line 25581 contains an incorrect operand. The ``addi'' RISC-V instruction format is ``addi rd, rs1, const,'' where:

\begin{enumerate}
    \item \texttt{rd} is the valid destination register;
    \item \texttt{rs1} is the first operand register;
    \item \texttt{const} is a value of 12 bits.
\end{enumerate}

This instruction is shown in Listing \ref{lst:incorrect_op}. Analyzing the instruction, it's possible to verify that the last operand \texttt{s0} is not a constant. As a result, a compiler error occurs.

\begin{listing}[h]
\caption{Incorrect operand in ``addi'' instruction.}
\label{lst:incorrect_op}
\begin{minted}[frame=single]{nasm}
andi s5,t1,s0 # line 25581 in test.S
\end{minted}
\end{listing}

\subsubsection{Solution}

To fix this bug, two solutions are possible:

\begin{enumerate}
 \item Change \texttt{s0} to a 12-bit constant.
 \item Change the ``addi" instruction to ``add."
\end{enumerate}

To maintain the pattern of ``test.S," which is testing only the ``add" instruction, the code was updated with the instruction with solution number 2), as presented in Listing \ref{lst:incorrect_op_fix}. Note that the operands stayed the same, and now it is a valid instruction.

\begin{listing}[h]
\caption{Fix Listing \ref{lst:incorrect_op} instruction.}
\label{lst:incorrect_op_fix}
\begin{minted}[frame=single]{nasm}
add s5, t1, s0 # line 25581 in test.S
\end{minted}
\end{listing}

By implementing these fixes, both bugs were resolved.
